{\Huge $ \ttlfnt{5e^{x+y}}$}: Searching over Mathematical Content in Digital Libraries

### 2015-04-26 jcdl2015/paper/main.tex
Capitalized title

\title{  {\Huge $ \ttlfnt{5e^{x+y}}$}: Searching over mathematical content in digital libraries}

@@

\begin{figure}
\centering
\begin{minipage}{.55\textwidth}
  \includegraphics[width=0.95\linewidth]{images/figures/results_interface.png}
  \captionof{figure}{Result page.}
  \label{fig:test2}
\end{minipage}
\end{figure}

>>>>

\title{  {\Huge $ \ttlfnt{5e^{x+y}}$}: Searching over Mathematical Content in Digital Libraries}

@@

\begin{figure}
\centering
\begin{minipage}{.55\textwidth}
  \includegraphics[width=0.95\linewidth]{images/figures/results_interface_alt.png}
  \captionof{figure}{Result page.}
  \label{fig:test2}
\end{minipage}
\end{figure}
